Corotating Dust Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-06-28 paper/ms.tex
update ms

		\vspace{-0.45cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f1b.pdf}
		}
	\end{center}
		\vspace{-0.3cm}
	\caption{
		{\bf Complex quasiperiodic variables (CQVs)}:
		{\it Top:} Phase-folded TESS light curves of three CQVs.  Each is
		stacked over one month.  Gray are raw 2-minute data; black bins to
		300 points per cycle.  Periods in hours are in the bottom right of
		each panel.  In order left-to-right, the objects are LP 12-502
		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
		425933644 (Sector~28).
		{\it Bottom:} Plausible cartoon models for the phenomenon.  The
		dust clump scenario seems most plausible, given
		the stability of the dips, the lack of observed infrared
		excesses, and the challenge of producing broadband opacity variations
		with only ionized hydrogen in the prominence scenario.
	}
	\label{fig:f1}
\end{figure*}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f2.pdf}
    \vspace{-0.7cm}
		\caption{
      {\bf CQVs found in the TESS 2-minute data.}
      Phased TESS light curves over one month are shown for \ngoods\
      CQVs.
      Gray are raw 2-minute data;
			black bins to 300 points per cycle.  Each panel is labelled by
      the TIC identifier, the TESS sector number, and the period in hours.
      The ordering is discussed in Section~\ref{sec:catalog}
		}
		\label{fig:singlemosaic}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.9\textwidth]{lc_mosaic_dlt150_good_allchangers_2count_showtitles.png}
		\vspace{-0.2cm}
		\caption{
			{\bf Evolution of CQVs}: ``Before and
			after'...  Panels
			in the top two rows are separated by two years
			($\approx$$10^3$ cycles); each panel shows one month.
			Periods are listed in hours. 
			{\bf todo: fix the plot and the caption.}
			%			\vspace{-0.8cm}
		}
		\label{fig:evoln}
	\end{center}
\end{figure*}

\subsection{Evolution over adjacent sectors, \& LP 12-502}
\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.9\textwidth]{TIC_402980664_P18.5611_2min_phase_timegroups_mosaic_ymin-4.8_ymax3.pdf}
		\vspace{-0.45cm}
		\caption{
			Evolution of LP 12-502 ($P$=18.6\,h) at fixed period and
			epoch over three years. 
			Each panel shows one (stacked) TESS orbit; small text denotes relative cycle number.
			There are 200 binned black points per cycle.
			The TESS pointing law dictates time gaps; larger gaps tend to
			yield larger shape changes.
			The dips usually evolve over tens to hundreds of cycles.
			However cycles 1233-1264 show a dip that ``switched'' from a depth
			and duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than
			one cycle.
		}
		\label{fig:lp}
	\end{center}

@@

\subsubsection{LP 12-502 observations}
While many CQVs had multiple sectors of adjacent or nearly-adjacent data
LP 12-502 (TIC 402980664; $d$=21\,pc, $J$=9.4,
$T$=11.1) stood out as an outlier among the CQV class.
Figure~\ref{fig:lp} shows all available data from Sectors
18, 19, 25, 26, 53, 58, and 59; the star was observed at 120-second
cadence whenever it was observable by TESS.
Measuring the PDM peak period over each sector independently yielded
an average $\langle P \rangle = 18.5560$\,hr, with a difference
between the maximum and minimum sector-level period of about one minute.
Based on this range, the period is therefore stable to at least one
minute ($\pm$0.017\,hr) over the three year baseline.
However, in detail, a period shift of $\pm$1\,minute yields major
phase drifts over the 3 year baseline; that time interval
corresponds to roughly 1/1000$^{\rm th}$ of a period; we have
observed 1500 cycles.
The achievable period precision, $\sigma_{\rm P}$, can be estimated as
\begin{equation}
  \sigma_{\rm P} = \frac { \sigma_{\rm \phi} P } { N_{\rm baseline} },
\end{equation}
for $N_{\rm baseline}$ the number of cycles in the observed baseline and
$\sigma_{\phi}$ the phase precision with which any one feature (e.g.~a
dip) can be tracked.
Assuming $\sigma_{\rm phi} \approx 0.01$ yields an expected period precision
$\sigma_{\rm P} \approx 0.45 {\rm sec} \approx 1.2\times 10^{-4}\,{\rm hr}$.
By visually fine-tuning over a grid in period, we eventually 
found $P=18.5611 \pm 0.0001$\,hr, which seems to track certain
features in the LP 12-502 light curve over its entire baseline.

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{tic4029_segments.pdf}
		\vspace{-0.2cm}
		\caption{
      {\bf LP 12-502 light curve}, where each time chunk represents one TESS orbit.
      Flares are drawn in gray.
      The red vertical lines highlight apparently instantaneous state changes in
      the shape of the dip pattern.
      The light curve is binned to 15-minute intervals so that
      there are 96 points per day.  Data gaps with more than one missing 15-minute
      cadence appear in white.
		}
		\label{fig:lplc}
	\end{center}
\end{figure*}

>>>>

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f1b.pdf}
		}
	\end{center}
		\vspace{-0.3cm}
	\caption{
		{\bf Complex quasiperiodic variables (CQVs)}:
		{\it Top:} Phase-folded TESS light curves of three CQVs.  Each is
		stacked over one month.  Gray are raw 2-minute data; black bins to
		300 points per cycle.  Periods in hours are in the bottom right of
		each panel.  In order left-to-right, the objects are LP 12-502
		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
		425933644 (Sector~28).
		{\it Bottom:} Plausible cartoon models for the phenomenon.  The
		dust clump scenario seems most plausible, given
		the stability of the dips, the lack of observed infrared
		excesses, and the challenge of producing broadband opacity variations
		with only ionized hydrogen in the prominence scenario.
	}
	\label{fig:f1}
\end{figure*}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f2.pdf}
    \vspace{-0.7cm}
		\caption{
      {\bf CQVs found in the TESS 2-minute data.}
      Phased TESS light curves over one month are shown for \ngoods\
      CQVs.
      Gray are raw 2-minute data;
			black bins to 300 points per cycle.  Each panel is labelled by
      the TIC identifier, the TESS sector number, and the period in hours.
      Objects are ordered such that sources with the most TESS data available are
       on top (see Section~\ref{sec:catalog}).
		}
		\label{fig:singlemosaic}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f3.pdf}
		\vspace{-0.6cm}
		\caption{
		{\bf CQVs keep their periods but change their shapes.}
      32 of our \ngoods\ CQVs from Figure~\ref{fig:singlemosaic} 
      had 120-second cadence TESS data available for
      a baseline of at least two years; the 27 brightest are shown here.
      Each panel shows one sector of TESS data, and is phased to its deepest minimum in flux.
      Each panel's title shows the TIC identifier and approximate period in hours.
      Text insets show the TESS sector numbers, which generally span two years, or at least
      1{,}000 cycles.
      The vertical scale is fixed across sectors to clarify shape changes.
		}
		\label{fig:evoln}
	\end{center}
\end{figure*}

\subsection{Evolution over adjacent sectors, \& LP 12-502}

\begin{figure*}[!tp]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f4.pdf}
		\vspace{-0.4cm}
		\caption{
			{\bf LP 12-502 (TIC~402980664) light curve}, where each time chunk represents one TESS orbit.
			Data were acquired in Sectors 18-19, 25-26, 53, and 57-58.
			Flares are drawn in gray.
			The red vertical lines highlight apparently instantaneous state changes in
			the shape of the dip pattern.
			The light curve is binned to 15-minute intervals so that
			there are 96 points per day.  Data gaps with more than one missing 15-minute
			cadence appear in white.
		}
		\label{fig:lplc}
	\end{center}
\end{figure*}

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.9\textwidth]{TIC_402980664_P18.5611_2min_phase_timegroups_mosaic_ymin-4.8_ymax3.pdf}
		\vspace{-0.45cm}
		\caption{
			Evolution of LP 12-502 ($P$=18.6\,h) at fixed period and
			epoch over three years. 
			Each panel shows one (stacked) TESS orbit; small text denotes relative cycle number.
			There are 200 binned black points per cycle.
			The TESS pointing law dictates time gaps; larger gaps tend to
			yield larger shape changes.
			The dips usually evolve over tens to hundreds of cycles.
			However cycles 1233-1264 show a dip that ``switched'' from a depth
			and duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than
			one cycle.
		}
		\label{fig:lp}
	\end{center}

@@

\subsubsection{LP 12-502 observations}
While many CQVs had multiple sectors of adjacent or nearly-adjacent data
LP 12-502 (TIC 402980664; $d$=21\,pc, $J$=9.4,
$T$=11.1) stood out as an outlier among the CQV class.
Figure~\ref{fig:lplc} shows all available data from Sectors
18, 19, 25, 26, 53, 58, and 59; the star was observed at 120-second
cadence whenever it was observable by TESS.
Figure~\ref{fig:lp} shows the same data, grouped into successive
TESS orbits spanning half a lunar month each.
Measuring the PDM peak period over each sector independently yielded
an average $\langle P \rangle = 18.5560$\,hr, with a difference
between the maximum and minimum sector-level period of about one minute.
Based on this range, the period is therefore stable to at least one
minute ($\pm$0.017\,hr) over the three year baseline.
However, in detail, a period shift of $\pm$1\,minute yields major
phase drifts over the 3 year baseline; that time interval
corresponds to roughly 1/1000$^{\rm th}$ of a period; we have
observed 1500 cycles.
The achievable period precision, $\sigma_{\rm P}$, can be estimated as
\begin{equation}
  \sigma_{\rm P} = \frac { \sigma_{\rm \phi} P } { N_{\rm baseline} },
\end{equation}
for $N_{\rm baseline}$ the number of cycles in the observed baseline and
$\sigma_{\phi}$ the phase precision with which any one feature (e.g.~a
dip) can be tracked.
Assuming $\sigma_{\rm phi} \approx 0.01$ yields an expected period precision
$\sigma_{\rm P} \approx 0.45 {\rm sec} \approx 1.2\times 10^{-4}\,{\rm hr}$.
By visually fine-tuning over a grid in period, we eventually 
found $P=18.5611 \pm 0.0001$\,hr, which seems to track certain
features in the LP 12-502 light curve over its entire baseline.

@@
